Approximation as Differentiation

### 2025-05-05 appendix/notes/auto-diff.tex
\int with a param notation for Grothendieck.

\subsubsection{Automatic differentiation via the Grothendieck construction}

Let $X, Y, Z$ range over sets and $U, V, W$ range over finite vector spaces. Recall that the category
$\Fam(\FinVect) = \Grothendieck{}\Fam(-, \FinVect)$ (\defref{grothendieck:Grothendieck}) has:
\begin{itemize}
\item as objects, all pairs $(X, \{V_x\}_{x \in X})$ of a set $X$ and an object of $\Fam(X,\FinVect)$;
\item as morphisms $(X, \{V_x\}_{x \in X}) \to (Y, \{W_y\}_{y \in Y})$, all pairs $(f, \partial f)$ of
functions $f: X \to Y$ and families of morphisms $\{\partial f_x: V_x \to W_{f(x)}\}_{x \in X}$
in $\Fam(X,\FinVect)$.
\end{itemize}

>>>>

\subsubsection{Automatic differentiation via category of families}

Let $X, Y, Z$ range over sets and $U, V, W$ range over finite vector spaces. Recall that the category
$\Fam(\FinVect) = \Grothendieck{X}\Fam(X, \FinVect)$ (\defref{grothendieck:Grothendieck}) has:
\begin{itemize}
\item as objects, all pairs $(X, \{V_x\}_{x \in X})$ of a set $X$ and an object of $\Fam(X,\FinVect)$;
\item as morphisms $(X, \{V_x\}_{x \in X}) \to (Y, \{W_y\}_{y \in Y})$, all pairs $(f, \partial f)$ of
functions $f: X \to Y$ and families of morphisms $\{\partial f_x: V_x \to W_{f(x)}\}_{x \in X}$
in $\Fam(X,\FinVect)$.
\end{itemize}
